\begin{thebibliography}{99}

\bibitem{tensorflow}
Mart\'{\i}n~Abadi et~al., \textit{{TensorFlow}: Large-scale machine learning on heterogeneous systems,} (Software available from tensorflow.org),  2015.

\bibitem{bvae}
Christopher~P. Burgess, Irina Higgins, Arka Pal, Loic Matthey, Nick Watters,
  Guillaume Desjardins, and Alexander Lerchner, 
\textit{Understanding disentangling in $\beta$-vae,}
\url{arXiv:1804.03599}, 2018.

\bibitem{Keras}
Fran\c{c}ois Chollet et~al.,
\newblock \textit{Keras},
\newblock \url{https://keras.io}, 2015.

\bibitem{original-VAE}
Carl Doersch,
\newblock \textit{Tutorial on variational autoencoders},
\newblock \url{arXiv:1606.05908}, 2016.



\bibitem{VAE}
Kevin Frans,
\newblock \textit{Variational autoencoders explained},
\newblock \url{http://kvfrans.com/variational-autoencoders-explained/}, 2016,
\newblock \textsl{Let\"oltve:} 2018-10-19.

\bibitem{original-GAN}
Ian~J. Goodfellow, Jean Pouget-Abadie, Mehdi Mirza, Bing Xu, David
  Warde-Farley, Sherjil Ozair, Aaron Courville, and Yoshua Bengio,
\newblock \textit{Generative adversarial networks},
\newblock \url{arXiv:1406.2661}, 2014.

\bibitem{Autoencoder}
Seungchul Lee, \textit{Autoencoder},
\url{http://i-systems.github.io/HSE545/machin learning all/Workshop/CAE/image_files/AE_arch2.png} \newblock \textsl{Let\"oltve:} 2018-11-25.

\bibitem{ConvNet}
Andrej Karpathy,
\newblock \textit{Convolutional neural networks for visual recognition},
\newblock \url{http://cs231n.github.io/convolutional-networks/}, 2018,
\newblock \textsl{Let\"oltve:} 2018-09-30.

\bibitem{Dsprite}
Loic Matthey, Irina Higgins, Demis Hassabis, and Alexander Lerchner,
\newblock\textit{ Dsprites: Disentanglement testing sprites dataset},
\newblock \url{https://github.com/deepmind/dsprites-dataset/}, 2017.

\end{thebibliography}
